%! TEX root = main.tex

\title{\normalsize%
    Red Hat Certified Instructor at Extraordy,\\Bachelor's degree at Politecnico di Milano
}
\maketitle

\section{Professional Experiences}
\cventry{\faIcon{graduation-cap}\hfill 2023}
    {Red Hat Certified Instructor}
    {}
    {}
    {}
    {}
\cventry{\faIcon{redhat}\hfill}
    {Red Hat Certified Engineer}
    {EX294}
    {}
    {}
    {}
\cventry{\faIcon{redhat}\hfill 2022}
    {Red Hat Certified Specialist in Enterprise Application Server Administration}
    {EX248}
    {}
    {}
    {}
\cventry{\faIcon{redhat}\hfill 2021}
    {Red Hat Certified System Administrator}
    {EX200}
    {}
    {}
    {}
\cventry{2020 - present}
    {Certified Dedicated Engineer}
    {``Extraordy Ltd''}
    {Milano (MI) 20123 Italy}
    {full-time employment}
    {The employee is involved in research and study activities, and he is also driven into sharing the acquired knowledge and skills with his colleagues. During his everyday activities, he works with the following technologies: Ansible, OpenShift, Satellite, RHEL, JBoss EAP.}
\cventry{2018}
    {Linux back-end Sysadmin}
    {``LM Networks Ltd''}
    {Lomazzo (LM) 22074 Italy}
    {full-time educational internship}
    {The intern was involved in both management and day-to-day support of the internal IT team, into research and development activities and into testing Hashicorp tool's capabilities.}

\section{Education}
\cventry{\faIcon{graduation-cap}\hfill 2015-2022}
    {Bachelor's degree}
    {``Politecnico di Milano''}
    {Milan (MI) 20133 Italy}
    {Computer Science and Engineering}
    {He attended the bachelor's degree courses in Computer Science and Engineering with intense application and aptitude for Information Technology and Telecommunications classes.}
\cventry{2010-2015}
    {High School}
    {Ettore Majorana}
    {Latina (LT) 04100 Italy}
    {Scientific orientation}
    {Attended his high school degree demonstrating great interests in scientific subjects; obtained his school-leaving certificate by discussing a paper entitled ``The impact of the gesture''.}

\section{Core skills}
\cvcomputer{\textbf{Languages}}{C++, Assembly, Java, Python, LaTeX, Bash, RegEx, VB.NET, C\#, PowerShell, HTML5, CSS, SQL.}
    {\textbf{Virtualization}}{Docker, Podman, Vagrant, Virtualbox, LibVirt, QEMU, VMWare.}
\cvcomputer{\textbf{DevOps}}{Git, Ansible, OpenShift, Kubernetes, JBoss EAP, Consul, Nomad, Prometheus, Grafana.}
    {\textbf{Electronics}}{Arduino, MicroPython, Espressif, Circuit Design, LoRa, BLE, Raspberry Pi.}

\section{Language skills}
\cvlanguage{English}{B2}
    {Achieved the FCE with Cambridge ESOL in 2013}
\cvlanguage{French}{A2}
    {Achieved the DELF certificate in 2010}
\cvlanguage{Italian}{Mother-tongue}
    {}

\pagebreak

\section{More information}
    \vspace{-0.1cm}
    \sethintscolumnlength{2cm}
    \subsection{Teamwork experiences}
    \begin{itemize}
        \item Took part in the \textbf{EY Cyber Incident Race 2019}, experiencing the activities to be carried out as an IT consultant team member, and working with colleagues having different study career backgrounds.
        \item Become an active member of the \textbf{Politecnico Open unix Labs} since July 2018; with the other members, he prepares lectures and workshops concerning programming languages and open source technologies.
        \item Got involved in the ‘\textbf{Interactive IoT and Smart Object Design}’ workshop, organized at Politecnico di Milano by professor Maristella Matera.
        \item Participated in CTF security competitions as a member of the \textbf{Tower of Hanoi} team, developing mind flexibility and problem-solving skills.
        \item Attended a \textbf{cybersecurity workshop} on binary exploitation and cryptography by Tower of Hanoi, developing interests in this subject by making contact with students from master's degree and PhD's, who are in the cybersecurity field.
        \item Took part in \textbf{hackathons} about the Internet of Things at Politecnico di Milano, meeting students from other countries (e.g. China, Spain, and India), making contact and working with them, learning how to develop a solution in a time and resource constrained situation.
        \item Volunteered as an \textbf{educator} at the ‘Don Bosco’ church of Latina for two years, learning how to cooperate with fellow peers and how to schedule activities and share roles among the members of a community, and how to deal with younger and older people.
    \end{itemize}

    \bigskip
    \subsection{Personal interests}
    \cvcomputer{\textbf{Arduino}}{Lover of the Arduino ecosystem since 2015, hacker of ESP8266 based platforms.}
        {\textbf{LaTeX}}{Advanced knowledge of LyX editor and \LaTeX~publishing workflow.}
    \cvcomputer{\textbf{Drummer}}{Has been playing since 2008, and achieved a merit certificate, released by Ettore Mancini; he was the drummer in a group since November 2015, for two years and a half.}
        {\textbf{Self-hosting}}{He is passionate in trying out and deploying free and open source solutions for continuous integration and system administration; he built a custom ``infrastructure'' to secure his data and customize the services he needs.}
    \cvcomputer{\textbf{VR/AR}}{Since 2020, has been playing Kinemotic Studio's Audio Trip and has been exploring the possibilities of AR for working better in a distracting and space-constrained environment.}
        {\textbf{Remote VDI}}{To better accommodate his remote working necessities, in 2021 he started to experiment with his home-made remote desktop infrastructure solution, through KVM, Tailscale, Moonlight and Sunshine.}

    \bigskip
    \subsection{Pubblications}
    \cvline{\faIcon{github}~\httplink[GitHub]{github.com/Procsiab/ns-workbook}}
        {Network Security workbook**}
    \cvline{\faIcon{github}~\httplink[GitHub]{github.com/Procsiab/ns-2019}}
        {Lecture notes from Network Security course**}
    \cvline{\faIcon{github}~\httplink[GitHub]{github.com/Procsiab/psi-2019}}
        {Lecture notes from Probability and Statistics course**}
    \cvline{\faIcon{github}~\httplink[GitHub]{github.com/Procsiab/fda-2018}}
        {Lecture notes from Foundations of Control Engineering course**}
    \cvline{\faIcon{github}~\httplink[GitHub]{github.com/Procsiab/ffs-2017}}
        {Lecture notes from Foundations of Applied Physics course**}
    \cvline{}{(\emph{** All the notes are in Italian language.})}
